---
title: "kyoto restaurant"
output: html_document
---

```{r}
pkgs = c("units","shinyWidgets","xml2","leaflet","htmltools","forcats")
for (pkg in pkgs){
  if (!(pkg %in% installed.packages()[, 1])){
    install.packages(pkg)
  }
}
library(dplyr)
library(tidyr)
library(purrr)
library(stringr)
library(forcats)
library(units)
library(shiny)
library(shinythemes)
library(shinyWidgets)
library(leaflet)
library("xml2")
library(htmltools)
library(ggplot2)
```

Load CSV File 

The dataset is downloaded from Kaggle. The raw data contains 14 features of 895 restaurants in Kyoto. The features include English and Japanese names, the nearby station, first and secondary food category which the restaurant belongs to, the price range and rating for dinner and lunch respectively, and location in longtitude and latitude.

```{r}
Kyoto_Restaurant_raw = read.csv("Kyoto_Restaurant_Info.csv")
```

Clean Data
The size of the dataset is relatively small. Even though the information it contains is self-demonstrated, some cleaning is still helpful for our shiny app. 
-We did cleaning for price range and made them into factors
-We made other features as factors as well
```{r}
#function
## clean function
clean_price = function(price){
  str_remove_all(price,"￥") %>% 
    str_replace("～","-") %>% 
    str_replace("^ -","0-") %>% 
    str_replace("30000-","30000+")
}
clean_category =function(category){
  category = category %>% 
    gsub("Bistro","Bar",.) %>%
    gsub("Beer garden","Beer",.) %>% 
    gsub("Beer bar","Beer",.) %>% 
    gsub("Wine bar","Bar",.) %>% 
    gsub("Traditional Café","Cafe",.) %>% 
    gsub("Champon Noodle","Ramen",.) %>% 
    gsub("Chinese hot pot / fire pot", "Chinese hot pot",.) %>% 
    gsub("Dandan noodles","Chinese",.) %>% 
    gsub("Dumplings","Chinese",.) %>% 
    gsub("Korean cuisine","Korea",.) %>% 
    gsub("Modern French","French",.) %>% 
    gsub("Pork ","",.) %>% 
    gsub("Stand ", "",.) %>% 
    gsub("Standing style s","S",.) %>% 
    gsub("Sukiyaki","Japanese hot pot",.) %>% 
    gsub("Thailand cooking", "Thailand",.) %>% 
    gsub("Udon Suki","Udon",.) %>% 
    gsub("Western Cuisine","Western",.)
}


Kyoto_Restaurant =Kyoto_Restaurant_raw %>% 
  mutate(
    Station = as.factor(Station),
    FirstCategory = as.factor(FirstCategory),
    SecondCategory = as.factor(SecondCategory),
    Category = clean_category(FirstCategory) %>% as.factor(),
    DinnerPrice = clean_price(DinnerPrice) %>% as.factor(),
    LunchPrice  = clean_price(LunchPrice) %>% addNA() %>% as.factor())

```
In order the give readers a brief introduction of the restautants in Kyoto, we try to visualize it in two ways: the type of food and correspondent number of restaurants and the location of reataurants.
In the first graph, we can see that certain types of food has much more number than others, such as Izkaya(Tavern) and BBQ beef.
In the second graph, we can see that the average rating among different types of food varies.
From third graph, the number of nearby reataurants of different stations are showed. We can find that those stations located in shopping center and tourism areas have more nearby restaurants, such as Kyoto station(the Main Railway Station) and Shijo(shopping center)

However, since there are so many types of food and stations, these diagrams seem to be a little messy. It would be better if we can summarize the type of food and the metro line which the stations belong to, thus giving a clearer view of these restaurants. 

Create a Shiny App
```{r}
shinyApp(
  ui = fluidPage(
    theme = shinytheme('united'),
    navbarPage(
      "Kyoto Restaurant",
      tabPanel(
        "Search Restaurant",value = 'Search Restaurant',
        fluidRow(
          column(
            3,
            #Select Station
            pickerInput("station", h5("Select the station closest to your ideal restaurant"),
                        choices = levels(Kyoto_Restaurant$Station),options = list(`actions-box` = TRUE),multiple = TRUE),
            #Select Food Category
            checkboxInput("choose_first_category","Select the food category"),
            conditionalPanel(
              "input.choose_first_category == true",
              selectInput("first_category",label = h5("Select the food category"),
                        choices = levels(Kyoto_Restaurant$Category),multiple = TRUE)),
            #Select Second Food Category
            conditionalPanel(
              "input.choose_first_category == true",
              checkboxInput("choose_second_category","Optional: select the second food category")),
            conditionalPanel(
              "input.choose_second_category == true && input.choose_first_category == true",
              selectInput("second_category",label = h5("Select the second food cetegory"),
                          choices = levels(Kyoto_Restaurant$SecondCategory))),
            #Choose Dinner or Lunch
            radioButtons("dinner_or_lunch",label =h5(NULL),choices = list("Dinner","Lunch")),
            #Select Dinner Price
            conditionalPanel(
              "input.dinner_or_lunch =='Dinner'",
              radioButtons("price_rough",label=h5("Select the Price"),
                         choices = list("￥","￥￥", "￥￥￥", "￥￥￥￥","￥￥￥￥￥"))),
            conditionalPanel(
              "input.dinner_or_lunch =='Dinner' && input.price_rough == '￥'",
              checkboxGroupInput("price_range1", label = h5("Select the price range(JPY)"),
                                 choices = levels(Kyoto_Restaurant$DinnerPrice)[1:2],
                                 selected = levels(Kyoto_Restaurant$DinnerPrice)[1:2])),
            conditionalPanel(
              "input.dinner_or_lunch =='Dinner' && input.price_rough == '￥￥'",
              checkboxGroupInput("price_range2", label = h5("Select the price range(JPY)"), 
                                 choices = levels(Kyoto_Restaurant$DinnerPrice)[c(5,7,9)],
                                 selected = levels(Kyoto_Restaurant$DinnerPrice)[c(5,7,9)])),
            conditionalPanel(
              "input.dinner_or_lunch =='Dinner' && input.price_rough == '￥￥￥'",
              checkboxGroupInput("price_range3", label = h5("Select the price range(JPY)"), 
                                 choices = levels(Kyoto_Restaurant$DinnerPrice)[10:12],
                                 selected = levels(Kyoto_Restaurant$DinnerPrice)[10:12])),
            conditionalPanel(
              "input.dinner_or_lunch =='Dinner' && input.price_rough == '￥￥￥￥'",
              checkboxGroupInput("price_range4", label = h5("Select the price range(JPY)"),
                                 choices = levels(Kyoto_Restaurant$DinnerPrice)[3:4],
                                 selected = levels(Kyoto_Restaurant$DinnerPrice)[3:4])),
            conditionalPanel(
              "input.dinner_or_lunch =='Dinner' && input.price_rough == '￥￥￥￥￥'",
              checkboxGroupInput("price_range5", label = h5("Select the price range(JPY)"), 
                                 choices = levels(Kyoto_Restaurant$DinnerPrice)[c(6,8)],
                                 selected = levels(Kyoto_Restaurant$DinnerPrice)[c(6,8)])),
            #Select Dinner Rating
            conditionalPanel(
              "input.dinner_or_lunch =='Dinner'",
              sliderInput("dinner_rating",h5("Minimum rating"), min = as.numeric(3), max = as.numeric(4.16),value = 3.0)),
            #Select Lunch Price
            conditionalPanel(
              "input.dinner_or_lunch =='Lunch'",
              radioButtons("price_rough_lunch",label=h5("Select the Price"),
                         choices = list("￥","￥￥", "￥￥￥", "￥￥￥￥"))),
            conditionalPanel(
              "input.dinner_or_lunch =='Lunch' && input.price_rough_lunch == '￥'",
              checkboxGroupInput("price_range1_l", label = h5("Select the price range(JPY)"),
                                 choices = levels(Kyoto_Restaurant$LunchPrice)[1:2],
                                 selected = levels(Kyoto_Restaurant$LunchPrice)[1:2])),
            conditionalPanel(
              "input.dinner_or_lunch =='Lunch' && input.price_rough_lunch == '￥￥'",
              checkboxGroupInput("price_range2_l", label = h5("Select the price range(JPY)"), 
                                 choices = levels(Kyoto_Restaurant$LunchPrice)[5:7],
                                 selected = levels(Kyoto_Restaurant$LunchPrice)[5:7])),
            conditionalPanel(
              "input.dinner_or_lunch =='Lunch' && input.price_rough_lunch == '￥￥￥'",
              checkboxGroupInput("price_range3_l", label = h5("Select the price range(JPY)"), 
                                 choices = levels(Kyoto_Restaurant$LunchPrice)[8:10],
                                 selected = levels(Kyoto_Restaurant$LunchPrice)[8:10])),
            conditionalPanel(
              "input.dinner_or_lunch =='Lunch' && input.price_rough_lunch == '￥￥￥￥'",
              checkboxGroupInput("price_range4_l", label = h5("Select the price range(JPY)"),
                                 choices = levels(Kyoto_Restaurant$LunchPrice)[3:4],
                                 selected = levels(Kyoto_Restaurant$LunchPrice)[3:4])),
            #Select Lunch Rating
            conditionalPanel(
              "input.dinner_or_lunch =='Lunch'",
              sliderInput("lunch_rating",h5("Minimum rating"), min = as.numeric(3), max = as.numeric(4.11),value = 3.0)),
            #Add an Action Button
            actionButton("search", h5("Search"))),
          column(
            9,
            leafletOutput("leaf", width = "100%", height = 500),
            uiOutput("links"),
            tableOutput("restaurant")),
            textOutput("error"))
    ),
    tabPanel(
      "Graph", value = "Graph",
      fluidRow(
        column(1),
       plotOutput("number"),
       plotOutput("rating"),
       plotOutput("station"),
        column(1)))
    
    #insert tabPanel here
    )
  ),
  
  
  server = function(input, output, session){
    # Filter the restaurant, returning a data frame
    restaurants = eventReactive(input$search,{
      ## Generate temp variables for input values
      station = input$station
      first_category = input$first_category
      second_category = input$second_category
      
      rough_price = input$price_rough
      if (rough_price == "￥" )
        dinner_price = input$price_range1
      if (rough_price == "￥￥")
        dinner_price = input$price_range2
      if (rough_price == "￥￥￥")
        dinner_price = input$price_range3
      if (rough_price =="￥￥￥￥")
        dinner_price = input$price_range4
      if (rough_price == "￥￥￥￥￥")
        dinner_price = input$price_range5
      dinner_rating = input$dinner_rating
        
      rough_price_lunch = input$price_rough_lunch
      if (rough_price_lunch == "￥" )
        lunch_price = input$price_range1_l
      if (rough_price_lunch == "￥￥")
        lunch_price = input$price_range2_l
      if (rough_price_lunch == "￥￥￥")
        lunch_price = input$price_range3_l
      if (rough_price_lunch =="￥￥￥￥")
        lunch_price = input$price_range4_l
      lunch_rating = input$lunch_rating
      
      ## Apply filters
      rd = Kyoto_Restaurant %>% 
        filter(
          Station %in% station,
          DinnerPrice %in% dinner_price,
          DinnerRating >=dinner_rating) 
      
      rl = Kyoto_Restaurant %>% 
        filter(
          Station %in% station,
          LunchPrice %in% lunch_price,
          LunchRating >=lunch_rating) 
      
      if (input$dinner_or_lunch == "Dinner")
        r = rd
      if (input$dinner_or_lunch == "Lunch")
        r = rl
      
      # Optional filter
      if (input$choose_first_category ==TRUE){
        r = r %>% 
          filter(Category %in% first_category) %>% 
          arrange()
        if (input$choose_second_category ==TRUE){
          r = r %>% 
            filter(SecondCategory == second_category) %>% 
            arrange()}
        else return(r)
        }
      else return(r)
      
      r = as.data.frame(r)
   })
    
    #print notice if empty df of restaurant is returned
    output$error =  renderText({
      if (nrow(restaurants()) == 0)
        return("No restaurants matching the search. Please reselect the filters")
    })
      
    #Set output of a map indicating the selected restaurants
    output$leaf = renderLeaflet({
      leaflet(restaurants()) %>%
        setView(lng = restaurants()[1,14], lat = restaurants()[1,13],zoom = 50) %>% 
        addTiles() %>%
        addMarkers(~Long, ~Lat, popup = paste(restaurants()$JapaneseName, "<br>",
                                              restaurants()$Name, "<br>",
                                              "Rating:",restaurants()$TotalRating,"<br>",
                                              "Nearby Station:",restaurants()$Station))})
    
    state = reactiveValues(
      observers = list()
    )
    
    observeEvent(input$search, {
      
      # Destroy existing observers
      for(i in seq_along(state$observers)) {
        state$observers[[i]]$destroy()
      }
      
      #Assign headlines to the links
      ui_elems = map(
        seq_len(nrow(restaurants())), function(i) fluidRow(actionLink(paste0("link",i),restaurants()[i,3]))
      )
      output$links = renderUI(fluidPage(ui_elems))
      
      # Reset and create new observers for each of our links
      state$observers = map(
        seq_len(nrow(restaurants())), 
        function(i) {
          label = paste0("link",i)
          observeEvent(
            input[[label]], 
            { #create modal dialog
              showModal(modalDialog(
                tags$header(h4(restaurants()[i,3])),
                tags$div(
                  tags$br(restaurants()[i,2]),
                  tags$br(paste0("Rating:",restaurants()[i,9])),
                  tags$br(paste0(restaurants()[i,15],", ",restaurants()[i,6])),
                  tags$br(paste0("Station nearby: ",restaurants()[i,4])),
                  tags$br(paste0("Dinner Price:",restaurants()[i,7],", Dinner Rating:",restaurants()[i,10])),
                  tags$br(paste0("Lunch Price:",restaurants()[i,8],", Lunch Rating:",restaurants()[i,11]))),
                easyClose = TRUE))
            }, 
            ignoreInit = TRUE
          )
        }
      )
    })
    
    #Set output of a restaurant table
    output$restaurant = renderTable({
      output_restaurants = restaurants() %>% 
        select(Name,JapaneseName,DinnerPrice,LunchPrice)
      })
    
    #show the restaurants number of different kinds
    output$number = renderPlot({
        Kyoto_Restaurant_num = Kyoto_Restaurant_raw %>%
        group_by(FirstCategory) %>%
        summarise(num = n()) %>%
        arrange(desc(num))
        Kyoto_Restaurant_num$FirstCategory <- as_factor(Kyoto_Restaurant_num$FirstCategory)
        
        number = Kyoto_Restaurant_num
        ggplot(data=number,aes(x = FirstCategory, y = num)) +
          geom_col(alpha = 0.5) +
          theme_bw() +
          ggtitle("Number of different restaurant") +
          theme(axis.text.x=element_text(angle = 45, hjust = 1, size = 10))
      })
    
     #show the rating of different kind of foods
     output$rating = renderPlot({
      Kyoto_Restaurant_rating = Kyoto_Restaurant_raw %>%
        group_by(FirstCategory) %>%      
          mutate(TotalRating = as.character(TotalRating),
                 TotalRating = as.double(TotalRating)) %>%
          mutate(count = n(),
                 sum_rating = sum(TotalRating),
                 TotalRating = as.double(TotalRating),
                 average_rating = sum_rating/count) %>% 
          arrange(desc(average_rating))
      
      
      rating = Kyoto_Restaurant_rating
      ggplot(rating,aes(x = FirstCategory, y = average_rating )) +
          geom_point(alpha = 0.5, size = 2) +
          ggtitle("Rating of different restaurant") +
          theme(axis.text.x=element_text(angle = 45, hjust = 1,size = 10))  
    
    })

    #Restaurant distribution among railway stations
    output$station = renderPlot({
      Kyoto_station = Kyoto_Restaurant_raw %>%
        group_by(Station) %>%      
          summarise(num = n()) %>%
          arrange(desc(num)) 
      
      sta = Kyoto_station
      ggplot(sta,aes(x=Station, y = num)) +
           geom_col(alpha = 0.4) +
           theme_bw() +
           ggtitle("Restaurant distribution among railway stations") +
          theme(axis.text.x=element_text(angle = 45, hjust = 1,size = 10))  
    
    })
  }
)
```



